---
title: "Vis I"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
```

Import the weather data.
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USW00022534", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2021-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = case_match(
      id, 
      "USW00094728" ~ "CentralPark_NY", 
      "USW00022534" ~ "Molokai_HI",
      "USS0023B17S" ~ "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

Export data.
```{r}
write_csv(weather_df, file = "data/weather_df.csv")
```

Making our first plot.
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```

```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

```{r}
ggp_weather_scatterplot = 
  weather_df |>
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()

ggp_weather_scatterplot
```


Check why some rows are missing.
```{r}
weather_df |>
  filter(is.na(tmax))
```


## Fancier scatterplot
```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .3, size = .8) + 
  geom_smooth(se = FALSE)
```


Where you define the aesthetics can matter.
```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name), alpha = .3, size = .8) + 
  geom_smooth(se = FALSE)
```


Use faceting real quick
```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .3) + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```


Let's make a somewhat more interesting scatterplot.
```{r}
weather_df|>
  ggplot(aes(x = date, y = tmax, color = name, size = prcp)) +
  geom_point(alpha = .3) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```


Learning Assesment
```{r}
weather_df |> 
  filter(name == "CentralPark_NY") |> 
  mutate(
    tmax_fahr = tmax * (9 / 5) + 32,
    tmin_fahr = tmin * (9 / 5) + 32
  ) |> 
  ggplot(aes(x = tmin_fahr, y = tmax_fahr)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) 
```


## Small things
```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name), alpha = .3, size = .8) +
  geom_smooth(se = FALSE)
```

```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex()
```


```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(color = "blue")
```


## Univariate plots
```{r}
weather_df |>
  ggplot(aes(x = tmin)) +
  geom_histogram()
```

```{r}
weather_df |>
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram(position = "dodge")
```


How would I fix this?
```{r}
weather_df |>
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram() +
  facet_grid(. ~ name)
```


Maybe a density plot?
```{r}
weather_df |>
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = .3)
```

```{r}
weather_df |>
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_boxplot()
```


Violin plots
```{r}
weather_df |>
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin()
```


Ridge plot
```{r}
weather_df |>
  ggplot(aes(x = tmin, y = name)) +
  geom_density_ridges()
```

Learning Assessment
```{r}
weather_df |>
  filter(prcp > 10) |>
  ggplot(aes(x = prcp, fill = name)) +
  geom_density(alpha = .3)

weather_df |>
  ggplot(aes(x = prcp, y = prcp)) +
  geom_boxplot()

weather_df |>
  filter(prcp > 10, prcp < 1000) |> 
  ggplot(aes(x = prcp, fill = name)) +
  geom_density(alpha = .3)
```


## Savings and embedding plots
```{r}
ggp_weather = 
  weather_df |>
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point()
  
ggsave("plots/ggp_weather.pdf", ggp_weather, width = 8, height = 6)
```


Embedding plots
```{r, fig.width = 6, fig.asp = .6}
weather_df |>
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point()
```

